Impact of grids and dynamical cores in CESM2.2 on the surface mass balance of the Greenland Ice Sheet

### 2022-03-12 arcticgrids.tex
updated figures

@@

\begin{figure}[t]
\begin{center}
\begin{tabular}{cccc}
         \includegraphics[width=60mm]{figs/temp_grisres_dxoverglc.pdf}&
         \includegraphics[width=60mm]{figs/temp_grisres_error.pdf} \\
\end{tabular}
\end{center}
\caption{.}
\label{fig:grisdx}
\end{figure}

>>>>

\begin{figure}[t]
\begin{center}
         \includegraphics[width=130mm]{figs/temp_grisres.pdf}
\end{center}
\caption{The spatial properties of the GrIS for different grids in this study. (Left) approximate average grid spacing over GrIS, (right) GrIS area error, computed as the relative differences from a 4km dataset used to create the CESM ice masks.}
\label{fig:grisdx}
\end{figure}

@@
